Open archaeology, open source?

### 2023-09-19 analysis/_03-data_methodology.qmd
Add tbl-repo-licenses

**NOTE:** Add a breakdown on licensing practices.
```{r tbl-repo-licenses}
```

>>>>

```{r tbl-repo-licenses}
#| tbl-cap: Summary of licenses used by projects with GitHub repositories.
oarch |>
  hoist(gh_repo_info, license = list("license", 1, "name")) |>
  count(license) |>
  mutate(license = replace_na(license, "None detected"))
  arrange(-n) |>
  gt() |>
    cols_label(license = "License", n = "N")
```
